\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-02-27 paper.tex
Update on Overleaf.

Underworlds is used 
%within the European MuMMER project
to be able to assess visibility and knowledge about objects, places and agents within the scene.

@@

A first client \textit{env\_provider} provides the environment set-up and allows to build a first \texttt{ENV} world where static objects/furnitures and walls are present. 
Then, the system cascades three worlds successively by the help of three clients. \textit{robot\_monitor} provides a first world where the robot is present. \textit{humans\_monitor} provides a new world where the humans are present (using~\cite{Khalidov_Idiap-RR-02-2017}). \textit{object\_monitor} provides a new world where the objects are present (using {\tt ar\_track\_alvar}\footnote{\url{http://wiki.ros.org/ar\_track\_alvar}). At this end we obtain a world \texttt{BASE}.

@@

@@

We are currently setting up this kind of network in the framework of the European project MuMMER where a Pepper robot is intended to handle interactive situations in a Mall in Finland. One of the situation is a guiding task where Pepper will help people to find their route by pointing them landmarks and explaining them how to reach a destination. The use of \uwds enables to get knowledge about what the customer sees (or has seen) or not and to handle the task accordingly. We plan also to be able to add information coming from the dialogue (e.g. if the customer says that he has seen a particular landmark that could consequently be added to his belief world). Moreover, we plan also to use alternative world ability given by \uwds (as explained in \ref{alter}) (e.g. to create a world where we put )would be able to infer a possible world where the customer will be put in front of the desired shop to be able to explain him what he will see at destination.

TODO LAAS: on est en train de reflechir a mettre dans l'exemple un nouvau monde simule (notre cas d'ecole c'est qu'on place le bonhomme en simule devant un magasin et on est capable de calculer ce qu'il verra en face de ce magasin) mais il faut qu'on le fasse coller avec l'exemple qu'on a

>>>>

\uwds is used 
%within the European MuMMER project
to be able to assess visibility and knowledge about objects, places and agents within the scene.

@@

A first client \textit{env\_provider} provides the environment set-up and allows to build a first \texttt{ENV} world where static objects/furnitures and walls are present. 
Then, the system cascades three worlds successively by the help of three clients. \textit{robot\_monitor} provides a first world where the robot is present. \textit{humans\_monitor} provides a new world where the humans are present (using~\cite{Khalidov_Idiap-RR-02-2017}). \textit{object\_monitor} provides a new world where the objects are present (using {\tt ar\_track\_alvar}\footnote{\url{http://wiki.ros.org/ar_track_alvar}}). At this end we obtain a world \texttt{BASE}.

@@

It has to be noticed that this knowledge could be wrong relatively to the current "real" state of the world, but it represents the monitored agent belief about the world.

@@

We are currently setting up this kind of network in the framework of the European project MuMMER where a Pepper robot is intended to handle interactive situations in a Mall in Finland. One of the situation is a guiding task where Pepper will help people to find their route by pointing them landmarks and explaining them how to reach a destination. The use of \uwds enables to get knowledge about what the customer sees (or has seen) or not and to handle the task accordingly. We plan also to be able to add information coming from the dialogue (e.g. if the customer says that he has seen a particular landmark that could consequently be added to his belief world). Moreover, we plan also to use alternative world ability given by \uwds (as explained in \ref{alter}) (e.g. to create a world where we put the customer in front of the desired shop to infer (and be able to explain him) what he will see at destination).
